### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/1.tex
chap2 in progress
progress

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process of Carbon Nano-wires]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.37]{./Figures/CBNfingerprint.png}
\decoRule
\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to meso-scale structural features of synthetic polymers influence the emergence of specific micro-structural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.30]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

\begin{figure}[th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonAllotropesHybridization.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on sp Content]{Ternary phase diagram of amorphous carbon regions based on hybridization degree. Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013}.}
\label{fig:carbonAllotropesDiagram}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonAllotropesPorosityNOrder.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on Porosity and Structural Order]{Ternary phase diagram of amorphous carbon regions based on structure order and porosity. Regions are colored by the degree of crystalline order within the carbon structure. White represents highly ordered structures, whereas white represents disordered structures. \cite{Marsh1989, Hugh1994}}
\label{fig:carbonAllotropesPorosityNOrder}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonFiberDiameterComparison.png}
\decoRule
\caption[Diameter comparison of various types of fibrous carbon materials]{Various types of fibrous carbon materials bear different characteristics according to their molecular structure. Adapted from \cite{Vajtai2013}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

@@

Typically, carbon nano-fibers (CNFs) are synthesized by a combination of a patterning process and a pyrolysis process. CNFs fabricated by electrospinning of polymer solutions with electrostatic forces. Electrospun CNFs have characteristics such as high surface area, thin morphology with nano-scale diameters. The properties of electrospun fibers allow CNFs to be implemented in nano-sensing devices, energy storage applications, and tissue scafflods. \cite{Khanna2016, Ramakrishna2005, Reneker2000, Norris2000, Vozzi2002, Kim2003, Dersch2005} Several patterning techniques have been attempted to achieve the desired fiber morphology. In addition to electrospinning, CNFs have been also fabricated by two-photon polymerization (TPP) and photo-lithography techniques. \cite{CardenasBenitez2019} Cardenas et al. implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems.

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.50]{./Figures/typesOfNanoSensors.png}
\decoRule
\caption[Types of Nano-sensors]{Diagram examples of carbon-based nano-sensors. Adapted from \cite{BaudritJ2017}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

>>>>

\begin{figure}[!th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process of Carbon Nano-wires]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.37]{./Figures/CBNfingerprint.png}
\decoRule
\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to meso-scale structural features of synthetic polymers influence the emergence of specific micro-structural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.30]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonAllotropesHybridization.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on sp Content]{Ternary phase diagram of amorphous carbon regions based on hybridization degree. Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015, Vajtai2013}.}
\label{fig:carbonAllotropesDiagram}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonAllotropesPorosityNOrder.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on Porosity and Structural Order]{Ternary phase diagram of amorphous carbon regions based on structure order and porosity. Regions are colored by the degree of crystalline order within the carbon structure. White represents highly ordered structures, whereas white represents disordered structures. \cite{Marsh1989, Hugh1994}}
\label{fig:carbonAllotropesPorosityNOrder}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.65]{./Figures/carbonFiberDiameterComparison.png}
\decoRule
\caption[Diameter comparison of various types of fibrous carbon materials]{Various types of fibrous carbon materials bear different characteristics according to their molecular structure. Adapted from \cite{Vajtai2013}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

@@

Typically, carbon nano-fibers (CNFs) are synthesized by a combination of a patterning process and a pyrolysis process. CNFs fabricated by electrospinning of polymer solutions with electrostatic forces. Electrospun CNFs have characteristics such as high surface area, thin morphology with nano-scale diameters. The properties of electrospun fibers allow CNFs to be implemented in nano-sensing devices, energy storage applications, and tissue scafflods. \cite{Khanna2016, Ramakrishna2005, Reneker2000, Norris2000, Vozzi2002, Kim2003, Dersch2005} Several patterning techniques have been attempted to achieve the desired fiber morphology. In addition to electrospinning, CNFs have been also fabricated by two-photon polymerization (TPP) and photo-lithography techniques. \cite{CardenasBenitez2019} Cardenas et al. implemented TPP and conventional UV lithography to study the fabrication of CNFs within carbon micro-electromechanical systems (C-MEMS). The fabrication of these kind of carbon devices has been previously reported for teachniques, such as electrospinning and photoresist patterning by photolithography using SU-8. The typical fabrication process of C-MEMS begins with a spin-coating of a photoresist unto a substrate (typically SU-8), followed by patterning techniques with UV-exposure by photolithography. Followed by the development of the desired features solvent. Finally, the device is carbonized in a pyrolysis furnace in an inert environment. \cite{Pramanick2018a}

Near-field electrospinning can be regarded as complementary technique, by which polymeric nanofibers can be produced, since the structural geometries created photolithography are restricted by the diffraction limit. \cite{Pramanick2018a, Okazaki1991} SU-8 is designed to produce vitrous carbon structure via photolithography, it is not design for electrospinning procedures as it lacks the right viscosity and solution conductivity. Cardenas \cite{Cardenas2017} and Flores \cite{Flores2017} have adapted the SU-8 formulation by the addition of tetrabutylammonium tetrafluoroborate (TBF) and poly(ethylene oxide) (PEO). TBF was added to increase the solution conductivity and PEO provides the required viscosity. Both additions are required to yield smooth solution flow during electrospinning.

\begin{table}[ht]
\centering
\caption[Prepared Polymer Solutions in Previous Work]{Prepared Polymer Solutions in Previous Work \cite{Cardenas2017, Flores2017}}
\begin{tabular}{cccc}
\hline
\textbf{Sample} & \multicolumn{3}{c}{\textbf{Concentration} $wt\%$} \\
\hline
{} & \textbf{SU-8} & \textbf{PEO} & \textbf{TBF} \\
1 & 99.50 & 0.25 & 0.25 \\
2 & 99.00 & 0.50 & 0.50 \\
3 & 98.50 & 0.75 & 0.75 \\
4 & 98.00 & 1.00 & 1.00 \\
\hline
\end{tabular}
\label{tab:previousPreparedPolymerSolutions}
\end{table}

The thinnest fibers achieved by Cardenas \cite{Cardenas2017} were achieved with sample 1 of Table \ref{tab:previousPreparedPolymerSolutions}, with the following characteristics: a) Fiber yield rate of $81\%$; b) Fiber diameter before pyrolysis of $4.966 \mu m$; c) Fiber diameter after pyrolysis of $204 nm$; d) Average fiber length of $60.5 ± 4.3 \mu m$; and e) Fiber electrical resistance from $407 K \Omega$ to $1.727 M \Omega$. Cardenas results have areas of opportunity regarding the fiber yield rate and the high variability on the fiber electrical resistance. These undesirable characteristics could be a consequence of the addition of PEO to the solution. Figure \ref{fig:su8Components} illustrates the ingredients that comprise the SU-8 formulation. SU-8 based vitreous carbon is obtained after a pyrolysis process in which the oxygen already present in the SU-8 formulation allow the formation of close pores during annealing. However, the further addition of oxygen content present in the PEO molecules may be the cause of the low yield rate and high variability in electric resistivity from sample to sample.

\begin{figure}[!th]
\centering
\includegraphics[scale=0.50]{./Figures/su8Components.png}
\decoRule
\caption[Components of SU-8 2000 Series Resists]{Components of SU-8 2000 Series Resists. Adapted from \cite{Microchem2012}}
\label{fig:su8Components}
\end{figure}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.50]{./Figures/typesOfNanoSensors.png}
\decoRule
\caption[Types of Nano-sensors]{Diagram examples of carbon-based nano-sensors. Adapted from \cite{BaudritJ2017}}
\label{fig:diameterComparisonOfCarbonFibers}
\end{figure}

### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/2.tex
progress

@@

\begin{enumerate}
\item Case 1 : data is collected as is from literature. This procedure was implemented when the data is listed within tables and/or as text format.
\item Case 2 : data is only presented in a figure as plots.
\item Case 3 : data is not available in text format or plots, however Scanning Electron Microscopy Images (SEM) images are reported from the obtained fibers.
\end{enumerate}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.45]{./Figures/screenshotWebPlotDigitizer.png}
\decoRule
\caption[WebPlotDigitizer home-screen]{Open session of WebPlotDigitizer \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{github.com}}
\label{fig:screenshotWebPlotDigitizer}
\end{figure}

@@

Measurements were validaded with Camillo's, Gupta's, Jiang's, Min's, Sun's, Wang's, and Xue's \cite{Camillo2013, Gupta2007, Jiang2018, Min2013, Sun2006a, Wang2015, Xue2014} results as those authors reported both, a SEM image and the measured fiber diameter. For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}. The measurement error of the developed script is about $3.2\%$ in avg. It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length. In most cases, measurements at the end of the fibers are thicker than the ones measured u¿in the center.

@@

Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \cite{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES). One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage. On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachey2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.

@@

@@

>>>>

\begin{figure}[!th]
\centering
\includegraphics[scale=0.45]{./Figures/DifferentElectrospinningMethods.png}
\decoRule
\caption[Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution]{Different Electrospinning Methods in Terms of Spatial Control, Fiber Throughput and Resolution. Adapted from \cite{Tourlomousis2017}}
\label{fig:DifferentElectrospinningMethods}
\end{figure}

As depicted in Figure \ref{fig:DifferentElectrospinningMethods}, solution electrospinning yields fiber with higher resolution than melt electrospinning techniques, and near-field electrospinning offers greater spacial control on the deposition of fibers than the far-field technique. Moreover, solution electrospinning often involves the use of toxic solvents, whereas melt electrospinning is a solvent free process but with extra complexity as a heater needs to be installed. \cite{Tourlomousis2017}

@@

\begin{enumerate}
\item Case 1 : data is collected as is from literature. This procedure was implemented when the data is listed within tables and/or as text format.
\item Case 2 : data is only presented in a figure as plots.
\item Case 3 : data is not available in text format or plots, however Scanning Electron Microscopy (SEM) images are reported from the obtained fibers.
\end{enumerate}

@@

\begin{figure}[!th]
\centering
\includegraphics[scale=0.45]{./Figures/screenshotWebPlotDigitizer.png}
\decoRule
\caption[WebPlotDigitizer home-screen]{Open session of WebPlotDigitizer \href{https://github.com/ankitrohatgi/WebPlotDigitizer}{github.com}}
\label{fig:screenshotWebPlotDigitizer}
\end{figure}

@@

Measurements were validaded with Camillo's, Gupta's, Jiang's, Min's, Sun's, Wang's, and Xue's \cite{Camillo2013, Gupta2007, Jiang2018, Min2013, Sun2006a, Wang2015, Xue2014} results as those authors reported both, a SEM image and the measured fiber diameter. For instance, Figure \ref{fig:imageAnalysisToolValidation} shows in white the reported diameters by Min and in blue the diameters measured by the \emph{Python script}. The measurement error of the developed script is about $3.2\%$ in average. It is considerable to mention that the reported measurement error is mainly contributed to the fact that most fibers are not of the same diameter along the fiber length. In most cases, measurements at the end of the fibers are thicker than the ones measured u¿in the center.

@@

Looking at Figures \ref{fig:plt_Lm_vs_Dfiberm} and \ref{fig:plt_Phi0V_vs_Dfiberm}, the data points from Husain, Lee and Sonntag \cite{Husain2016, Lee2012, Sonntag2020} experimental results are outside the principal cluster since they implemented working distances around $10^{-1} \textrm{m}$, which is concidered to be the threshold between NFES and far-field electrospinning (FFES). One can observe that: a) in NFES fiber diameter increase with increasing applied voltage; and b) in FFES fiber diameter decrease with increasing applied voltage. On the other hand, data related to Liu's and Beachey's work \cite{Liu2014, Beachley2011} do not fit the main trend as they perform the electrospinning process with a rotating drum as the collector, instead of the typical xy stage.

@@

Electrospinning is a simple process to fabricate fibers of different morphology. However, the final morphology of a fiber depends on various solution, process, and ambient parameters (Table \ref{tab:nfesProcessParameters}) with interaction with rheology and fluid dynamics. Given the connection of various parameters, it is not trivial to derive a mathematical model to describe the complete electrospinning process. Current attempts involve limited models that can only describe the steady jet region for specific polymer solutions. \cite{Hohman2001a,Feng2002a,Reneker2000} From literature \cite{Greiner2008, Deitzel2001, Cui2007, Beachley2011} and as described in Figure \ref{fig:plt_corMat}, zero-shear viscosity, flow rate and applied voltage are the main drivers that determine the final fiber morphology and dimensions. Other parameters such as solution surface tension, conductivity and working distance have less impact on the electrospun fibers. \cite{Ramakrishna2005} As shown in Figures \ref{fig:plt_Qm3s_vs_Dfiberm} and \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, literature states that flow rate $Q$ and solution concentration $C_{polymer}$ are directly proportional to the fiber diameter $D_{fiber}$. \cite{Wang2008, McKee2004, Gupta2005}

As mentioned in the previous section, the correlation between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ is not well defined. Most authors posit that the fiber diameter decreases with increasing voltage. \cite{Yuan2004, Wang2009, Thompson2007, Sajeev2008, Mazoochi2011, MATARAM2011, Liu2007, Homayoni2009, Zhang2005} Nevertheless, other publications state the inverse correlation. \cite{Rojas2009, Jeun2007} This discrepancy between the final fiber diameter $D_{fiber}$ and the applied voltage $\Phi_0$ may be attributed to the fact that $\Phi_0$ is also related to the electric field $\Phi_0 / L$, which in turn is related to the working distance $L$. As the electric field $\Phi_0 / L$ increases, the electric field forces loose influence under the polymer jet as the increased force results into faster evaporation of the solvent promoting faster solidification. On the other hand, polymer concentration $C_{polymer}$, and conductivity $K$ also have an effect on the electric field. \cite{Thompson2007, Mohan2002}

On the other hand, Zhang et al., Kim et al., and Mituppatham et al. studied the relationship between the solution surface tension $\gamma$ and its conductivity $K$. \cite{Zhang2005, Kim2005, Mituppatham2004} Kim's and Mituppatham's work report a increase in fiber diameter with increasing conductivity in the polymer solution, while Zhang's reports the inverse relationship. The existing interdependence between the process and solution parameters adds complexity and ambiguity to the effect of each parameter. The fiber morphology not only depends on the process parameters, but also on the type of electrospinning process and on polymer-solvent system. \cite{Gadkari2014}

Helgeson and Wagner \cite{Helgeson2007} have presented an adimensional analysis to predict the fiber diameter with conservation equations of momentum, mass, electric charge and four dimensionless numbers: Peclet number $ \displaystyle Pe = \frac{2 \bar{\varepsilon} v_0}{K R_0} $, Reynold number $ \displaystyle Re = \frac{\rho v_0 R_0}{\eta_0} $, Weber number $ \displaystyle We = \frac{\rho {v_0}^2 R_0}{\gamma} $, and the dimensionless electric field strength $ \displaystyle \Psi = \frac{\bar{\varepsilon} {E_0}^2}{\rho {v_0}^2} $. Where $\bar{\varepsilon}$ is the dielectric permitivity of the atmosphere, $K$ the solution conductivity, $\rho$ the density, $\eta_0$ the zero-shear viscosity, $\gamma$ the surface tension, $E_0$ the applied electric field, $R_0$ the initial jet radius, and $v_0$ the initial jet velocity. Since $R_0$ and $v_0$ can neither be controlled nor measured, Helgeson arrived to a correlation between the electrostatic and viscous forces $\Pi_1$ describing the stress directing the polymer jet elongation from the source to the collector plate. \cite{Helgeson2007}

\begin{equation}\label{eqn:electroViscousRatio}
    \Pi_1 = Re Pe \Psi = \frac{2 {\bar{\varepsilon}}^2 {\Phi_0}^2}{K \eta_0 L^2}
\end{equation}

Ohnesorge number, resulting from the manipulation of the Reynolds number $Re$ and the Weber number $We$, is used to explain the behavior of the polymeric solution jet under small disturbances, due the voltage presence, leads to the capillary rupture of the fluid jet. \cite{Helgeson2007}

\begin{equation}\label{eqn:ohnesorgeNumber}
    Oh = \frac{{Re}^2}{We} = \frac{\eta_0}{\sqrt{\rho \gamma R_{jet}}}
\end{equation}

Where $ \displaystyle R_{jet} = R_f \sqrt{\frac{1}{w_s}} $ is the wet radius of the jet solution, which is calculated from the radius of the dry fiber $R_f$ and the mass fraction of the polymer in solution $w_s$. \cite{Helgeson2007}

@@

Figure \ref{fig:plt_Pi1_vs_Oh} plots the $\Pi_1$ and $Oh$ values reported by \cite{Helgeson2007} along with new data points from the previous data collection of NFES fiber diameters and process parameters. It is possible to observe the predominance of the viscous and the electrostatic forces within the solution by the magnitude $\Pi_1$ (Equation \ref{eqn:electroViscousRatio}), on the other hand $Oh$ (Equation \ref{eqn:ohnesorgeNumber}) reflects the capacity of the viscous forces over the polymeric jet, which allows stability in the electrospinning process. The data points gathered by Helgeson et al. are from far-field electrospinning studies, whereas the new data points belong to near-field electrospinning studies.

The collected data suggest that both types of electrospinning behave in a similar manner, where the FFES data fits better a linear behavior of slope $-1$. As the working distance closes in NFES, the data points fit a shallower slope with higher $\Pi_1$ values and lower $Oh$ values. This suggests that in NFES less viscous solutions have been used, since in long working distances a higher viscosity is needed to keep the integrity of the fiber in the whole traveling distance until it reaches the collector. For high $Oh$ values and elevated viscosity, the entanglement of the polymeric chains is higher, resulting in the formation of individual fibers; also, the jet is prone to faster solidification, due to an early evaporation of solvent, due to the resistance to the change of momentum, caused by the high viscosity in the polymeric solution, hence the need of higher voltages in FFES. Helgeson et al. suggest that with the following relationship in Equation \ref{eqn:ohnesorgeNumberRelationship} can be used to predict the fiber diameter, as in the trend in Figure \ref{fig:plt_Pi1_vs_Oh} $Oh$ has an inverse linear relationship with $\Pi_1$. \cite{Helgeson2007}

\begin{equation}\label{eqn:ohnesorgeNumberRelationship}
    \Pi_1 Oh = \frac{2 {\bar{\varepsilon}}^2 {\Phi_0}^2}{K L^2 \sqrt{\rho \gamma R_{jet}}} = 2.5 \pm 0.2 \times 10^{-8}
\end{equation}

The absence of the solution zero-shear viscosity in Equation \ref{eqn:ohnesorgeNumberRelationship} suggests that $\eta_0$ by its own is insufficient to predict the fiber diameter. The solution conductivity, process parameters and surface tension are the main drivers to describe the diameter of electrospun fibers. \cite{Helgeson2007}

### 2020-11-17 05_Thesis/THESIS_LaTeX/main.tex
progress

\noindent\enquote{\itshape Carbon is a simple element but ............... \\
\medskip 
One branch of chemistry is devoted to its compounds! \\
\medskip 
One branch of science is devoted to the many forms of the element as a solid material. \\
\medskip 
The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated, a closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
\end{center}

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
\include{./Chapters/5}

>>>>

\noindent\enquote{\itshape Carbon is a simple element but ............... \\
\medskip 
one branch of chemistry is devoted to its compounds! \\
\medskip 
... one branch of science is devoted to the many forms of the element as a solid material. \\
\medskip 
The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated. A closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
\end{center}

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
%\include{./Chapters/5}
